---
title: "Déterminer la taille d'un fichier"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)

```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Include some data examples in your package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.

- There already is a dataset in the "inst/" directory to be used in the examples below
-->

```{r development-dataset}
# Run all this chunk in the console directly
# There already is a dataset in the "inst/" directory
# Make the dataset file available to the current Rmd during development
pkgload::load_all(path = here::here(), export_all = FALSE)

# You will be able to read your example data file in each of your function examples and tests as follows - see chunks below
datafile <- system.file("nyc_squirrels_sample.csv", package = "fusen")
nyc_squirrels <- read.csv(datafile, encoding = "UTF-8")

nyc_squirrels

path <- system.file("nyc_squirrels_sample.csv", package = "fusen")

filesize <- file.size(path)
filename <- basename(path)

out <- data.frame(name = filename, size = filesize ) 
```


# Taille d'un fichier

La fonction `get_one_file_size()` permet de calculer la taille d'un fichier.
Elle prend les arguments suivants :

  - En entrée : un nom de fichier
  - En sortie : un `data.frame` avec le nom et la taille du fichir fourni.

<!--
Create a chunk for the core of the function

- The chunk needs to be named `function` at least
- It contains the code of a documented function
- The chunk can also be named `function-my_median` to make it easily
findable in your Rmd
- Let the `@examples` part empty, and use the next `examples` chunk instead to present reproducible examples

After inflating the template

-  This function code will automatically be added in a new file in the "R/" directory
-->

```{r function}
#' Obtenir la taille d'un fichier
#'
#' @param path A string : path of the file to be analysed.
#'
#' @return df_filesize A `data.frame` : name and size of the file pointed by `path`.
#' @export
#'
#' @examples
get_one_file_size <- function(path) {
  
filesize <- file.size(path)
filename <- basename(path)

df_filesize <- data.frame(name = filename, size = filesize ) 
return(df_filesize)
}
```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will automatically be added in the '@examples' part of our function above in the "R/" directory
- This example will automatically be added in the vignette created from this Rmd template
-->

```{r examples}


# Example with your dataset in "inst/"
datafile <- system.file("nyc_squirrels_sample.csv", package = "fusen")

get_one_file_size(datafile)
# data(sampledf)
# 
# temp_path <- tempfile(pattern = "test_filesize")
# temp_filepath <- file.path(temp_path,"sampledf.csv" )
# write.csv(x = sampledf, temp_filepath) 
# get_one_file_size(sampledf)


```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will automatically be added in the "tests/testthat/" directory
-->

```{r tests}
test_that("get_one_file_size works",{

nrowsquirrels <- get_one_file_size(system.file("nyc_squirrels_sample.csv", package = "toolboxfilebenoit")
)
  expect_equal(nrowsquirrels[["size"]],
               118993)
})
```

# Calculate the mean of a vector

<!--
There can be other functions, examples and tests in your flat template.
Each of them will be inflated in a different file, provided that there is a level-1 or level-2 section title to separate from previous functions.
-->

<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/get_one_file_size.Rmd", vignette_name = "Taille des fichiers")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
